### 2019-02-18 sections/intuition.tex
recap

The focus on collaboration gives rise to concepts like communication, concurrency and synchronisation.
Using tasks, however, they are meant to be used on a higher level of abstraction, which allows concise declarative description of patterns of collaboration, without worrying about the implementation details of communication.
By focussing on collaboration, tasks and \TOPHAT lead to high-level specifications closer to real-world workflows which, at the same time, can be used to generate distributive, multi-user applications to support such workflows.

To employ these patterns of collaboration, users need to communicate.
This motivates different forms of communication: with the environment, along control flow, and across control flow.

>>>>

To model collaboration, one needs communication, concurrency, and synchronisation.
In \TOP, collaboration is specified on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.

By focussing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate distributed, multi-user applications to support such workflows.
